---
title: "R Notebook"
output:
  html_document:
    df_print: paged
  html_notebook: default
  pdf_document: default
  word_document: default
---


```{r setup, include=FALSE}

#Sys.setlocale("LC_TIME", "C");
#sessionInfo()

knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.path = 'figures/', echo = FALSE, warning = FALSE, message = FALSE)

cat("\014")  # clear console
rm(list=ls(all=TRUE))

library(timevis)
library( timelineS )
library( timeDate )

```
28.02.2018 GDP has grown by 4.5 % in 2017 and by 4.2 % in the 4th quarter
28.02.2018 In January, retail trade turnover grew by 7.1 %
06.03.2018 In January, industrial output grew by 4.2 %
12.03.2018 Janvari precu arejas tirdzniecibas apgrozijums par 12,4 % lielaks neka pern
           In January foreign trade turnover in goods was 12.4 % larger than last year
21.03.2018 Razotaju cenu limenis rupnieciba februari palielinajas par 0,5 %
           In February level of producer prices in industry increased by 0.5 %
29.03.2018 Februari mazumtirdzniecibas apgrozijums pieauga par 3,7 %
           In February, retail trade turnover grew by 3.7 %
03.04.2018 Februari rupniecibas produkcijas apjoms pieauga par 8,7 %
           In February, industrial output grew by 8.7 %
09.04.2018 Februari precu arejas tirdzniecibas apgrozijums par 9,9 % lielaks neka pern
           In February foreign trade turnover in goods was 9.9 % larger than last year
10.04.2018 Videjais paterina cenu limenis gada laika palielinajas par 2,2 %
           During the year, the average level of consumer prices increased by 2.2 %





```{r}
gdp_4     = c( name = "GDP"     , period = "Q1" , date = "2018-02-28" )
retail_1  = c( name = "RETAIL"  , period = "I"  , date = "2018-02-28" )
surv_2    = c( name = "SURVINDU", period = "Q1" , date = "2018-02-28" )
iip_1     = c( name = "IIP"     , period = "I"  , date = "2018-03-06" )
upers_2   = c( name = "UPERS"   , period = "II" , date = "2018-03-09" )
vacancy_2 = c( name = "VACANCY" , period = "II" , date = "2018-03-09" )
exptot_1  = c( name = "EXPTOT"  , period = "I"  , date = "2018-03-12" )
ppi_2     = c( name = "PPI"     , period = "II" , date = "2018-03-21" )
retail_2  = c( name = "RETAIL"  , period = "II" , date = "2018-03-29" )
iip_2     = c( name = "IIP"     , period = "II" , date = "2018-04-03" )
exptot_2  = c( name = "EXPTOT"  , period = "II" , date = "2018-04-09" )
cpi_2     = c( name = "CPI"     , period = "III", date = "2018-04-10" )
upers_3   = c( name = "UPERS"   , period = "III", date = "2018-04-20" )
vacancy_3 = c( name = "VACANCY" , period = "III", date = "2018-04-20" )

data = list( gdp_4, retail_1, iip_1, upers_2,vacancy_2,exptot_1, ppi_2, retail_2, iip_2, exptot_2, cpi_2,upers_3,vacancy_3 )

dfdata <- data.frame(
  id      = seq(1, length(data) ),
  content = paste( sapply(data, "[", "name" ), sapply(data, "[", "period" ), sep = ":" ) ,
  start   = sapply(data, "[", "date" ),
  end     = rep(NA, length(data) )
)
dfdata
timevis(dfdata) 
```

### adopt a timelineS command to my wishes
```{r}

r1 = as.Date( "2017-12-31" )
r2 = as.Date( "2018-04-30" )

main = "Release timing"
xlab = NA
scale.above = T
scale.small = "5 days"
scale.format = "%b %d"
scale.font   = 1
scale.cex    = 0.75
scale.orient = 1
line.color = "gray44"
line.width = 1
scale.tickwidth = 1
label.color = "gray44"
h = 0

range.events = c( r1, r2 )

plot(NA, ylim = c(0, 1), xlim = range.events, ann = FALSE, axes = FALSE)
title(main = main, xlab = xlab)
ticks_small = seq( r1, r2, by = scale.small)
ticks_eom   = unique( as.Date( timeLastDayInMonth( xaxis_daily ) ) )

axis.Date(ifelse(scale.above == TRUE, 3, 1), at = ticks_small,
        format = scale.format, cex.axis = scale.cex, pos = h,
        lwd.tick = scale.tickwidth, col = line.color, font = scale.font,
        las = scale.orient, labels = FALSE, tck= 0.02 )
axis.Date(ifelse(scale.above == TRUE, 3, 1), at = ticks_eom,
        format = scale.format, cex.axis = scale.cex, pos = h,
        lwd.tick = scale.tickwidth, col = line.color, font = scale.font,
        las = scale.orient, labels = FALSE, tck= -0.05 )
text(x = ticks_small-2, par("usr")[3]*.9, labels = paste(format( ticks_small, scale.format ),' '), srt = 45, pos = 1, xpd = TRUE,cex=.7)

segments(as.Date("2018-02-28"), 0, as.Date("2018-02-28"), 0.8, col = label.color)
color <- shadepalette(grey(0.8), "blue", n = 50)
filledrectangle(wx = 12, wy = 0.1, col = color,mid = c( as.Date("2018-02-28"), 0.8), angle = 0)
text( as.Date("2018-02-28"), 0.8, "GDP:Q1", cex=0.75)


### check this: https://stackoverflow.com/questions/41967849/how-do-i-shift-axis-labels-to-the-left-so-that-they-are-aligned-with-tick-marks?rq=1


```


```{r}
mj_life
timelineS(mj_life, main = "Life of Michael Jackson", 
label.direction = "up", label.length = c(0.2,0.8,0.4,1.2), label.position = 3, 
line.color = "blue", label.color = "blue", point.color = "blue", pch = "-")

timelineB = function (df, main = NA, xlab = NA, buffer.days = 600, line.width = 5, 
    line.color = "gray44", scale = "year", scale.format = "%Y", 
    scale.font = 2, scale.orient = 1, scale.above = FALSE, scale.cex = 1, 
    scale.tickwidth = 2, labels = paste(df[[1]], df[[2]]), label.direction = "downup", 
    label.length = c(0.5, 0.5, 0.8, 0.8), label.position = c(1, 
        3), label.color = "gray44", label.cex = 0.8, label.font = 1, 
    label.angle = 0, pch = 20, point.cex = 1, point.color = "gray44") 
{
    if (!is.data.frame(df)) {
        stop("'df' must be a data frame")
    }
    df <- df[rowSums(is.na(df)) == 0, ]
    event.names <- df[[1]]
    event.dates <- df[[2]]
    if (label.direction == "downup") {
        d = c(-1, 1)
        h = 0
    }
    else if (label.direction == "updown") {
        d = c(1, -1)
        h = 0
    }
    else if (label.direction == "up") {
        d = 1
        h = -0.7
    }
    else if (label.direction == "down") {
        d = -1
        h = 0.7
    }
    else {
        d = c(-1, 1)
        h = 0
        print("incorrect label.direction, plot used default")
    }
    range.events <- range(min(event.dates) - buffer.days, max(event.dates) + 
        buffer.days)
    r1 <- range.events[1]
    r2 <- range.events[2]
    plot(NA, ylim = c(-1, 1), xlim = range.events, ann = FALSE, 
        axes = FALSE)
    title(main = main, xlab = xlab)
    points <- rep_len(d * label.length, length.out = nrow(df))
    events <- rep_len(label.position, length.out = nrow(df))
    segments(event.dates, h, event.dates, points + h, col = label.color)
    
    xaxis_at = seq(as.Date(paste0(lubridate::year(r1), 
        "-", lubridate::month(r1), "-", 1)), as.Date(paste0(lubridate::year(r2), 
        "-", lubridate::month(r2) + 1, "-", 1)), by = scale)
    
    axis.Date(ifelse(scale.above == TRUE, 3, 1), at = xaxis_at, 
        format = scale.format, cex.axis = scale.cex, pos = h, 
        lwd.tick = scale.tickwidth, col = line.color, font = scale.font, 
        las = scale.orient, labels = FALSE )
    text(x = xaxis_at, par("usr")[3]*.99, labels = paste(xaxis_at,' '), srt = 45, pos = 1, xpd = TRUE,cex=.7)
    abline(h = h, lwd = line.width, col = line.color)
    points(x = event.dates, y = points + h, pch = pch, cex = point.cex, 
        col = point.color)
    text(x = event.dates, y = points + h, labels = labels, cex = label.cex, 
        pos = events, font = label.font, srt = label.angle)
}


data_timeline <- data.frame(
  Events      = paste( sapply(data, "[", "name" ), sapply(data, "[", "period" ), sep = ":" ) ,
  Event_Dates = as.Date( sapply(data, "[", "date" ) )
)
timelineS(data_timeline, main = "Release schedule", 
label.direction = "up", label.length = c(0.2,0.8,0.4,1.2), label.position = 3, 
line.color = "blue", label.color = "blue", point.color = "blue", pch = "-")

timelineS(data_timeline[ 1:9, ],label.direction = "up", buffer.days = 10, scale = "week", scale.format = "%b %d", main = "Release timing",scale.font = 1,scale.cex = 0.75,scale.orient = 1)

```

```{r}
data <- data.frame(
  id      = 1:4,
  content = c("Item one"  , "Item two"  ,"Ranged item", "Item four"),
  start   = c("2016-01-10", "2016-01-11", "2016-01-20", "2016-02-14 15:00:00"),
  end     = c(NA          ,           NA, "2016-02-04", NA)
)
```



```{r}
myTimeline<-timevis(
         data.frame(id = 1:2,
                    content = c("one", "two"),
                    start = c("2016-01-10", "2016-01-12"))
     )
htmlwidgets::saveWidget(myTimeline, "myTimeLine.png", selfcontained = T)
```

```{r}
library( shape )
color <- shadepalette(grey(0.8), "blue", n = 50)
plot(NA, main = "filledrectangle", ylim = c(-1,1), xlim= c(-1,1)) #empty
filledrectangle(wx = 0.3, wy = 0.3, col = color,mid = c(0, 0), angle = 0)
text( 0, 0, "GDP:Q1", cex=0.75)
#textflag(mid = c(0.5, 0.5), radx = 0.2, rady = 0.2, lcol = "white", lab = "hello", cex = 1, font = 1)
#mtext( c(0,0))

library(grid)
plot(NA, main = "filledrectangle", ylim = c(-1,1), xlim= c(-1,1)) #empty
grid.roundrect(width=.1, height=.1, x = 0.5, y = 0.5)
grid.text("GDP:Q1")

box1 <- boxGrob(c("ISBN", "title", "pub"), x=0.3)
box2 <- boxGrob(c("ID", "name", "country"), x=0.7)
grid.draw(box1)
grid.draw(box2)



plot(NA, main = "filledrectangle", ylim = c(-1,1), xlim= c(-1,1)) #empty
grid.roundrect(width=.5, height=.5, name="rr")

theta <- seq(0, 360, length=50)
for (i in 1:50)
    grid.circle(x=grobX("rr", theta[i]),
                y=grobY("rr", theta[i]),
                r=unit(1, "mm"),
                gp=gpar(fill="black"))
```


